\documentclass[10pt]{deedy-resume-reversed}
\usepackage{amsmath}
\usepackage{fontspec}
\setmainfont{Noto Sans}
\setsansfont{Noto Sans}
\newcommand{\edit}[1]{#1}
\newenvironment{editblock}{}{}
\newcommand{\skillsec}[2]{\subsection{\edit{#1}}\edit{#2}\sectionsep}
\usepackage{fancyhdr}
\pagestyle{fancy}\fancyhf{}

% Tight spacing for one page
\renewcommand{\sectionsep}{\vspace{4pt}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\begin{document}


%================= HEADER =================
\namesection{Mohammad Machaka}{%
  \href{mailto:machaka.mohammad@gmail.com}{machaka.mohammad@gmail.com}
  ~~|~~ +33\,(0)\,7\,53\,37\,78\,23
  ~~|~~ Toulouse, FR
  ~~|~~ \href{https://mohammad.machaka.net}{mohammad.machaka.net}
  ~~|~~ \href{https://linkedin.com/in/mohammad-machaka-a63685172}{linkedin.com/in/mohammad-machaka-a63685172}
}

%============= TWO COLUMNS ===============
\begin{minipage}[t]{0.30\textwidth}

% ---- Profile ----
\section{Profile}
{\small
Systems-minded software and cloud engineer (AWS SAA-C03) deepening my systems perspective through the ISAE-SUPAERO SEN programme. I like clean logic, traceable systems, and work that lasts. My instinct is to bring order , to understand how each piece fits and make it simpler to change later. I’m steady under uncertainty, patient with details, and I like when a design feels elegant because it’s clear.
}
\sectionsep

% ---- Skills ----
\section{Skills}
{\normalsize
\skillsec{Systems Engineering}{
Requirements \& ICDs • V-model • V\&V • ISO/IEC 15288 • SysML/Capella • DOORS • Lifecycle \& traceability mindset
}

\skillsec{Data / Geospatial}{
Airflow/ETL orchestration • Rasterio/GDAL • Google Earth Engine • Data cleaning automation
}

\skillsec{Cloud / DevOps}{
AWS • Terraform • Kubernetes • Docker • Helm • GitHub Actions • IaC CI/CD pipelines
}

\skillsec{Software Engineering}{
Python/FastAPI • Node/Express (TypeScript) • C++ • REST API • PostGIS • MongoDB • Redis
}

\skillsec{Observability \& Reliability}{
Prometheus • Grafana • Alertmanager • SLOs \& alerting design • Service health dashboards • Tracing/logging culture
}
}
\sectionsep

% ---- Certifications ----
\section{Certifications}
\href{https://www.credly.com/badges/14c4b7ac-8600-4f71-9d0e-db6fc67de835/linked_in?t=t3enca}{AWS
 Solutions Architect — Associate (SAA-C03)}
 \sectionsep

% ---- Languages ----
\section{Languages}
English (Fluent) • French (Advanced) • Arabic (Fluent)
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.67\textwidth}

% ---- Experience ----
\section{Experience}

\runsubsection{Green Praxis}
\descript{| Cloud \& Data Engineer \textbullet\ Permanent}
\location{Jan 2025 -- Aug 2025 • Aix-en-Provence, FR}
\vspace{\topsep}
\begin{editblock}
\begin{tightemize}
\item Built and maintained \textbf{Airflow} DAGs to ingest multi-band Sentinel/Landsat scenes (cloud mask, reprojection, mosaics with Rasterio/GDAL) and recorded metadata in MongoDB.
\item Re-architected static tiles to \textbf{on-demand} rendering (FastAPI + Google Earth Engine + Redis): storage $\downarrow$80\%; map refresh $<$30 min; ingestion throughput $\uparrow\times6$.
\item Deployed \textbf{Prometheus/Grafana/Alertmanager} and instrumented services; alerts cover critical paths and support SLO tracking.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Terraform, AWS (EKS/EC2/S3/IAM), Kubernetes, Airflow, Prometheus, Grafana, FastAPI, Express.js (TS), Python, Docker, MongoDB, Redis
\sectionsep

\runsubsection{Airbus}
\descript{| Data Engineer \textbullet\ Internship/Apprenticeship}
\location{Jan 2023 -- Jun 2024 • Toulouse (Saint-Martin), FR}
\begin{editblock}
\begin{tightemize}
\item Developed \textbf{C++} real-time data streams for the OPTIMATE programme (high throughput; profiling \& robustness improvements).
\item Built \textbf{Python} ETL to collect, clean, and standardise HR datasets across 5 regions; reduced dashboard release time by $\sim$80\%.
\item Wrote concise indicators and runbooks so teams could reuse and maintain the pipelines.
\end{tightemize}
\end{editblock}
\textbf{Stack:} C++, Python, PostGIS, Workday, Postman, Azure DevOps, Jenkins, Docker
\sectionsep

\runsubsection{Murex Systems}
\descript{| Software Architect \textbullet\ Project Lead}
\location{May 2021 -- Jan 2022 • Beirut, LB}
\begin{editblock}
\begin{tightemize}
\item Designed a log-analysis demonstrator that surfaced \textbf{50+} previously unseen error patterns; improved time-to-root-cause.
\item Shipped an MVP on Kubernetes/Docker; led a 3-developer Scrum team (scope, reviews, delivery).
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python, Jenkins, Docker, Terraform, Kubernetes
\sectionsep

% ---- Education ----
\section{Education}

\runsubsection{ISAE-SUPAERO}
\descript{| Mastère Spécialisé\textsuperscript{\textregistered} Systems Engineering (SEN)}
\location{Sep 2025 -- Oct 2026 (exp.) • Toulouse}
\begin{editblock}
\begin{tightemize}
\item Focus: MBSE (SysML/Capella), requirements/ICDs, system architecture, V\&V, lifecycle (ISO/IEC 15288).
\end{tightemize}
\end{editblock}
\sectionsep

\runsubsection{Univ. Toulouse III — Paul Sabatier}
\descript{| M.Sc. Computer Science for Aerospace}
\location{Sep 2021 -- Jun 2024 • Toulouse}
\sectionsep

\runsubsection{American Univ. of Beirut}
\descript{| B.Sc. Computer Science \textbullet\ Minor Business Administration}
\location{Sep 2017 -- Jun 2020 • Beirut}
\begin{editblock}
\begin{tightemize}
\item LCPC Competitive Programming — 2\textsuperscript{nd} place; Valedictorian 2017/18.
\end{tightemize}
\end{editblock}
\sectionsep

% ---- Projects (selected) ----
\section{Projects (selected)}
\textbf{SUNSPEAR} — Systems Engineer: CONOPS; needs \(\rightarrow\) requirements; ICD skeletons; V\&V approach; review packets (SRR/PDR-like).\\
\textbf{HydroART} — Systems Engineer: Mission architecture; preliminary budgets; interface control; verification matrix.

\end{minipage}

\end{document}
