%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Mohammad Machaka — One-Page CV (truthful + JD-aligned, Airbus PDP/IDL)
% XeLaTeX • deedy-resume-reversed class
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{deedy-resume-reversed}
\usepackage{amsmath}
\usepackage{fontspec}
\setmainfont{Noto Sans}
\setsansfont{Noto Sans}
\newcommand{\edit}[1]{#1}
\newenvironment{editblock}{}{}
\newcommand{\skillsec}[2]{\subsection{\edit{#1}}\edit{#2}\sectionsep}
\usepackage{fancyhdr}
\pagestyle{fancy}\fancyhf{}

% Tight spacing for one page
\renewcommand{\sectionsep}{\vspace{4pt}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\begin{document}

%================= HEADER =================
\namesection{Mohammad Machaka}{%
  \href{mailto:machaka.mohammad@gmail.com}{machaka.mohammad@gmail.com}
  ~~|~~ +33\,(0)\,7\,53\,37\,78\,23
  ~~|~~ Toulouse, FR
  ~~|~~ \href{https://mohammad.machaka.net}{mohammad.machaka.net}
  ~~|~~ \href{https://linkedin.com/in/mohammad-machaka-a63685172}{linkedin.com/in/mohammad-machaka-a63685172}
}

%============= TWO COLUMNS ===============
\begin{minipage}[t]{0.30\textwidth}

% ---- Profile (plain, JD-aware, no over-claims) ----
\section{Profile}
{\small
Systems-minded software and cloud engineer (AWS SAA-C03) currently deepening my systems perspective through the ISAE-SUPAERO SEN programme.  
I enjoy designing tools that make complex data easier to trust and act on.  
Recent work includes building Airflow pipelines for satellite imagery, re-engineering map-tile services with Google Earth Engine, and deploying real-time monitoring that made issues visible before they became problems.  
I’m motivated by clarity, reliability, and turning data into insight that teams can actually use.
}

\sectionsep

% ---- Skills (concise, accurate, JD-friendly) ----
\section{Skills}
{\normalsize
\skillsec{Systems Engineering}{
Requirements & ICDs • V-model • V&V • ISO/IEC 15288 • SysML/Capella* • DOORS* • Lifecycle mindset & traceability
}

\skillsec{Data / Geospatial}{
Airflow/ETL orchestration • Rasterio/GDAL • Google Earth Engine • Data cleaning & automation
}
\skillsec{Cloud / DevOps}{
AWS  • Terraform • Kubernetes • Docker • Helm • GitHub Actions • IaC & CI/CD pipelines
}
\skillsec{Software Engineering}{
Python/FastAPI • Node/Express (TypeScript) • C++ • REST API design • PostGIS • MongoDB • Redis 
}
\skillsec{Observability & Reliability}{
Prometheus • Grafana • Alertmanager • SLOs & alerting design • Service health dashboards • Tracing/logging culture
}

}
\sectionsep

\sectionsep

% ---- Certifications ----
\section{Certifications}
\textbf{AWS Solutions Architect — Associate (SAA\=/C03)}\\
\sectionsep

% ---- Languages ----
\section{Languages}
English (Fluent) • French (Advanced) • Arabic (Fluent)
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.67\textwidth}

% ---- Experience ----
\section{Experience}

\runsubsection{Green Praxis}
\descript{| Cloud \& Data Engineer \textbullet\ Permanent}
\location{Jan 2025 -- Aug 2025 • Aix\=/en\=/Provence, FR}
\vspace{\topsep}

\begin{editblock}
\begin{tightemize}
  \item Built and maintained \textbf{Airflow} DAGs to ingest multi\=/band Sentinel/Landsat scenes (cloud mask, reprojection, mosaics with Rasterio/GDAL) and record metadata in MongoDB.
  \item Re\=/architected static tiles to \textbf{on\=/demand} rendering (FastAPI + Google Earth Engine + Redis): storage \(\downarrow\)\textbf{~80\%}; map refresh $<$30\,min; ingestion throughput \(\uparrow\)\textbf{$\times$6}.
  \item Deployed \textbf{Prometheus/Grafana/Alertmanager} and instrumented services; alerts cover critical paths and support SLO tracking.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Terraform, AWS (EKS/EC2/S3/IAM), Kubernetes, Airflow, Prometheus, Grafana, FastAPI, Express.js (TS), Python, Docker, MongoDB, Redis
\sectionsep

\runsubsection{Airbus}
\descript{| Data Engineer \textbullet\ Apprenticeship/Internship}
\location{Jan 2023 -- Jun 2024 • Toulouse (Saint\=/Martin), FR}
\begin{editblock}
\begin{tightemize}
  \item Developed \textbf{C++} real\=/time data streams for the OPTIMATE programme (high throughput; profiling and robustness improvements).
  \item Built \textbf{Python} ETL to collect, clean, and standardise HR datasets across 5 regions; reduced dashboard release time by \textbf{\(\sim\)80\%}.
  \item Wrote concise indicators and runbooks so teams could reuse and maintain the pipelines.
\end{tightemize}
\end{editblock}
\textbf{Stack:} C++, Python, PostGIS, Workday, Postman, Azure DevOps, Jenkins, Docker
\sectionsep

\runsubsection{Murex Systems}
\descript{| Software Architect \textbullet\ Project Lead}
\location{May 2021 -- Jan 2022 • Beirut, LB}
\begin{editblock}
\begin{tightemize}
  \item Designed a log\=/analysis demonstrator that surfaced \textbf{50+} previously unseen error patterns; improved time\=/to\=/root\=/cause.
  \item Shipped an MVP on Kubernetes/Docker with Terraform CI/CD; led a 3\=/developer Scrum team (scope, reviews, delivery).
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python, Jenkins, Docker, Terraform, Kubernetes
\sectionsep

% ---- Education (right column) ----
\section{Education}
% simple hyphen
\runsubsection{ISAE-SUPAERO}
\descript{| Mastère Spécialisé\textsuperscript{\textregistered} Systems Engineering (SEN)}
\location{Sep 2025 -- Oct 2026 (exp.) • Toulouse}

\begin{editblock}
\begin{tightemize}
  \item Focus: MBSE (SysML/Capella), requirements/ICDs, system architecture, V\&V, lifecycle (ISO/IEC 15288).
\end{tightemize}
\end{editblock}
\sectionsep

\runsubsection{Univ. Toulouse III — Paul Sabatier}
\descript{| M.Sc. Computer Science for Aerospace}
\location{Sep 2021 -- Jun 2024 • Toulouse}
\sectionsep

\runsubsection{American Univ. of Beirut}
\descript{| B.Sc. Computer Science • Minor Business Adminstration}
\location{Sep 2017 -- Jun 2020 • Beirut}
\begin{editblock}
\begin{tightemize}
  \item LCPC Competitive Programming — 2\textsuperscript{nd} place; Valedictorian 2017/18.
\end{tightemize}
\end{editblock}
\sectionsep

% ---- Projects (selected) ----
\section{Projects (selected)}
\textbf{SUNSPEAR} — Systems Engineer: CONOPS; needs\(\rightarrow\)requirements; ICD skeletons; V\&V approach; review packets (SRR/PDR\=/like). \\
\textbf{HydroART} — Systems Engineer: Mission architecture; preliminary budgets; interface control; verification matrix.

\end{minipage}

\end{document}

