\documentclass[10pt]{deedy-resume-reversed}
\usepackage{amsmath}
\usepackage{fontspec}
\setmainfont{Noto Sans}
\setsansfont{Noto Sans}
\newcommand{\edit}[1]{#1}
\newenvironment{editblock}{}{}
\newcommand{\skillsec}[2]{\subsection{\edit{#1}}\edit{#2}\sectionsep}
\usepackage{fancyhdr}
\pagestyle{fancy}\fancyhf{}

% Tight spacing for one page
\renewcommand{\sectionsep}{\vspace{4pt}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\begin{document}

%================= HEADER =================
\namesection{Mohammad Machaka}{%
\href{mailto:machaka[.mohammad@gmail.com](mailto:.mohammad@gmail.com)}{[machaka.mohammad@gmail.com](mailto:machaka.mohammad@gmail.com)}
~~|~~ +33,(0),7,53,37,78,23
~~|~~ Toulouse, FR
~~|~~ \href{[https://mohammad.machaka.net}{mohammad.machaka.net}](https://mohammad.machaka.net}{mohammad.machaka.net})
~~|~~ \href{[https://linkedin.com/in/mohammad-machaka-a63685172}{linkedin.com/in/mohammad-machaka-a63685172}](https://linkedin.com/in/mohammad-machaka-a63685172}{linkedin.com/in/mohammad-machaka-a63685172})
}

%============= TWO COLUMNS ===============
\begin{minipage}[t]{0.30\textwidth}

% ---- Profile ----
\section{Profile}
{\small
Systems-minded software & cloud engineer (AWS SAA/C03) completing the ISAE-SUPAERO SEN master in MBSE. I build clear interfaces, reliable data flows, and demos that make complex systems easy to grasp. Recent work covers Airflow pipelines for EO data, on-demand tile services, and dashboards & runbooks adopted by non-technical teams. Strong at turning requirements into architecture, verification, and robust code (Python, TypeScript, Java).
}
\sectionsep

% ---- Skills ----
\section{Skills}
{\normalsize
\skillsec{Systems Engineering}{
MBSE (SysML/Capella) • requirements • architecture • behaviour analysis • V&V • ICDs • traceability • PLM/CM
}
\skillsec{Software}{
Python • JavaScript/TypeScript (Node/Express) • Java • C++ • REST APIs • integrations • test planning
}
\skillsec{Cloud & DevOps}{
AWS • Terraform • Kubernetes • Docker • GitHub Actions • IaC • CI/CD
}
\skillsec{Data & Geo}{
Airflow • Rasterio/GDAL • Google Earth Engine • STAC • MongoDB • Redis • PostGIS
}
\skillsec{Enablement}{
Stakeholder demos • documentation • runbooks • technical talks
}
}
\sectionsep

% ---- Certifications ----
\section{Certifications}
\textbf{AWS Solutions Architect — Associate (SAA/C03)}
\sectionsep

% ---- Languages ----
\section{Languages}
English (Fluent) • French (Advanced) • Arabic (Fluent)
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.67\textwidth}

% ---- Experience ----
\section{Experience}

\runsubsection{Green Praxis}
\descript{| Cloud & Data Engineer \textbullet\ Permanent}
\location{Jan 2025 -- Present • Aix-en-Provence, FR}
\vspace{\topsep}
\begin{editblock}
\begin{tightemize}
\item Re-architected static tiles to \textbf{on-demand} rendering (FastAPI + Google Earth Engine + Redis): storage $\downarrow$80%; map refresh $<$30 min; ingestion throughput $\uparrow\times6$.
\item Built \textbf{Airflow} DAGs for Sentinel/Landsat (cloud mask, reprojection, mosaics with Rasterio/GDAL), catalogued via STAC into MongoDB.
\item Defined API/interface contracts, \textbf{Prometheus + Grafana + Alertmanager} coverage, and produced demos & runbooks for internal teams.
\end{tightemize}
\end{editblock}
\textbf{Stack:} AWS (EKS/EC2/S3/IAM), Terraform, Kubernetes, Airflow, FastAPI, Node/Express (TS), Python, MongoDB, Redis
\sectionsep

\runsubsection{Airbus}
\descript{| Data Engineer \textbullet\ Internship/Apprenticeship}
\location{Jan 2023 -- Jun 2024 • Toulouse (Saint-Martin), FR}
\begin{editblock}
\begin{tightemize}
\item \textbf{Python} ETL standardising HR datasets across five regions; dashboard release time cut by $\approx$80% through quality gates & packaging.
\item One-month exchange on \textbf{OPTIMATE} (automated taxiing): mapped producers/consumers, interfaces & SLAs; delivered pipeline and observability.
\item Contributed \textbf{C++} improvements to real-time streams; documented indicators, runbooks, and handover material for stakeholders.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python, C++, PostGIS, Jenkins, Azure DevOps, Docker
\sectionsep

\runsubsection{Murex Systems}
\descript{| Software Architect \textbullet\ Project Lead}
\location{May 2021 -- Jan 2022 • Beirut, LB}
\begin{editblock}
\begin{tightemize}
\item Conceived a \textbf{log-analysis demonstrator} surfacing 50+ unseen error patterns and cutting time-to-root-cause.
\item Led a three-developer Scrum team; shipped on Kubernetes with Terraform CI/CD and automated tests.
\item Presented findings to stakeholders; maintained docs and enablement material for adoption.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python, Kubernetes, Docker, Terraform, Jenkins
\sectionsep

% ---- Education ----
\section{Education}

\runsubsection{ISAE-SUPAERO}
\descript{| Mastère Spécialisé\textsuperscript{\textregistered} Systems Engineering (SEN)}
\location{Sep 2025 -- Oct 2026 (exp.) • Toulouse}
\begin{editblock}
\begin{tightemize}
\item MBSE, requirements engineering, architecture, behaviour analysis, V&V, dependability, PLM/CM; case studies include Airbus A350 & Dassault Aviation.
\end{tightemize}
\end{editblock}
\sectionsep

\runsubsection{Univ. Toulouse III — Paul Sabatier}
\descript{| M.Sc. Computer Science for Aerospace}
\location{Sep 2021 -- Jun 2024 • Toulouse}
\sectionsep

\runsubsection{American Univ. of Beirut}
\descript{| B.Sc. Computer Science • Minor Business Administration}
\location{Sep 2017 -- Jun 2020 • Beirut}
\begin{editblock}
\begin{tightemize}
\item LCPC Competitive Programming — 2\textsuperscript{nd} place; Valedictorian 2017/18; AGFE Scholar.
\end{tightemize}
\end{editblock}
\sectionsep

% ---- Projects ----
\section{Projects (selected)}
\textbf{SUNSPEAR} — Systems Engineer: CONOPS; needs $\rightarrow$ requirements; ICD skeletons; V&V approach; SRR/SDR-like packets.\
\textbf{HydroART} — Systems Engineer: Mission architecture; subsystem decomposition; preliminary budgets; interface control; verification matrix.

\end{minipage}

\end{document}
