\documentclass[10pt]{deedy-resume-reversed}
\usepackage{amsmath}
\usepackage{fontspec}
\setmainfont{Noto Sans}
\setsansfont{Noto Sans}
\newcommand{\edit}[1]{#1}
\newenvironment{editblock}{}{}
\newcommand{\skillsec}[2]{\subsection{\edit{#1}}\edit{#2}\sectionsep}
\usepackage{fancyhdr}
\pagestyle{fancy}\fancyhf{}

% Tight spacing for one page
\renewcommand{\sectionsep}{\vspace{4pt}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\begin{document}

%================= HEADER =================
\namesection{Mohammad Machaka}{%
\href{mailto:machaka.mohammad@gmail.com}{machaka.mohammad@gmail.com}
~~|~~ +33 (0) 7 53 37 78 23
~~|~~ Toulouse, FR
}

%============= TWO COLUMNS ===============
\begin{minipage}[t]{0.30\textwidth}

% ---- Profile ----
\section{Profile}
{\small
Software \& cloud engineer (AWS SAA-C03) transitioning into Systems Engineering (ISAE-SUPAERO SEN). I deliver reliable Python 3.11 services, data pipelines, and UI/API interfaces with measurable SLOs and strong observability. Experience migrating legacy services, defining interfaces, and validating via automated non-regression tests (unit/integration, CI). Aerospace exposure through Airbus (data engineering) and CS for Aerospace M.Sc.
}
\sectionsep

% ---- Skills ----
\section{Skills}
{\normalsize
\skillsec{Systems Engineering}{
MBSE (SysML/Capella, in progress) • requirements • architecture • behaviour analysis • V\&V • ICDs • traceability • PLM/CM
}
\skillsec{Software}{
Python 3.11 • C++ • C\# • Java • TypeScript/Node (Express) • FastAPI • REST APIs • NumPy • Pandas • test planning
}
\skillsec{Cloud \& DevOps}{
AWS • Terraform • Kubernetes • Docker • GitHub Actions • Jenkins • Git/GitLab • IaC • CI/CD
}
\skillsec{Data \& Geo}{
Airflow • Rasterio/GDAL • Google Earth Engine • STAC • MongoDB • Redis • PostGIS
}
\skillsec{Enablement}{
Non-regression suites • documentation \& runbooks • stakeholder demos
}
}
\sectionsep

% ---- Certifications ----
\section{Certifications}
\textbf{AWS Certified Solutions Architect — Associate (SAA-C03)} \\
\href{https://www.credly.com/badges/14c4b7ac-8600-4f71-9d0e-db6fc67de835/linked_in?t=t3enca}{Credential}
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.67\textwidth}

% ---- Experience ----
\section{Experience}

\runsubsection{Green Praxis}
\descript{| Cloud \& Data Engineer \textbullet\ Permanent}
\location{Jan 2025 -- Present • Aix-en-Provence, FR}
\vspace{\topsep}
\begin{editblock}
\begin{tightemize}
\item Re-architected legacy static tiles to on-demand rendering (FastAPI + Google Earth Engine + Redis): storage $\downarrow$80\%; map refresh $<$30 min; ingestion throughput $\uparrow\times6$.
\item Built 15+ \textbf{Airflow} DAGs for Sentinel/Landsat (cloud mask, reprojection, mosaics with Rasterio/GDAL), catalogued via STAC into MongoDB.
\item Established interface contracts, dashboards \& alerts (Prometheus/Grafana/Alertmanager), and CI deploys; authored runbooks for non-regression and ops.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python 3.11, FastAPI, Node/Express (TS), Airflow, AWS (EKS/EC2/S3/IAM), Terraform, Kubernetes, MongoDB, Redis, Prometheus/Grafana
\sectionsep

\runsubsection{Airbus SAS}
\descript{| Data Engineer \textbullet\ Internship \& Apprenticeship}
\location{Jan 2023 -- Jun 2024 • Toulouse, FR}
\begin{editblock}
\begin{tightemize}
\item Standardised HR datasets with Python ETL; packaged repeatable deployments; dashboard release time $\downarrow\approx$80\% via automated quality gates.
\item OPTIMATE (automated taxiing) exchange: mapped producers/consumers, interfaces \& SLAs; delivered data-flow pipeline with targeted monitoring.
\item Implemented data validation and non-regression checks; documented indicators, interfaces, and handover runbooks.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python, PostGIS, Jenkins, Azure DevOps, Docker, Git
\sectionsep

\runsubsection{Murex Systems}
\descript{| Software Architect \textbullet\ Project Lead}
\location{May 2021 -- Jan 2022 • Beirut, LB}
\begin{editblock}
\begin{tightemize}
\item Conceived a log-analysis platform surfacing 50+ unseen error patterns and improving time-to-root-cause.
\item Led a 3-developer team; enforced reviews, CI/CD, and automated testing; shipped modular services with stable interfaces.
\item Drove requirements, milestones, and stakeholder demos; maintained technical documentation.
\end{tightemize}
\end{editblock}
\textbf{Stack:} Python, Kubernetes, Docker, Terraform, Jenkins, CI/CD
\sectionsep

% ---- Education ----
\section{Education}

\runsubsection{ISAE-SUPAERO}
\descript{| Mastère Spécialisé\textsuperscript{\textregistered} in Systems Engineering (SEN)}
\location{Sep 2025 -- Oct 2026 (expected) • Toulouse, FR}
\begin{editblock}
\begin{tightemize}
\item Focus: MBSE, requirements, system architecture, V\&V, dependability/safety, PLM/CM, project mgmt; tools: SysML/Capella, ARCADIA; case studies A350, Dassault.
\end{tightemize}
\end{editblock}
\sectionsep

\runsubsection{Univ. Toulouse III — Paul Sabatier}
\descript{| M.Sc. Computer Science for Aerospace}
\location{Sep 2021 -- Jun 2024 • Toulouse, FR}
\sectionsep

\runsubsection{American University of Beirut}
\descript{| B.Sc. Computer Science • Minor in Business Administration}
\location{Sep 2017 -- Jun 2020 • Beirut, LB}
\begin{editblock}
\begin{tightemize}
\item LCPC Programming Contest — Runner-up (2019); Valedictorian (2017/18); AGFE Scholarship.
\end{tightemize}
\end{editblock}
\sectionsep

% ---- Projects ----
\section{Projects (selected)}
\textbf{SUNSPEAR} — Systems Engineer: CONOPS; needs $\rightarrow$ requirements; ICDs; V\&V strategy; SRR/SDR-like packets.\
\textbf{HydroART} — Systems Engineer: Mission architecture; subsystem decomposition; mass/power/data budgets; interface control; verification matrix.

\end{minipage}

\end{document}