\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\begin{document}

%==================== HEADER ====================
\textbf{Mohammad Machaka}\\
16 Rue du Touch, 31170 Tournefeuille\\
Tournefeuille, France\\
+33\,(0)7\,53\,37\,78\,23\\
\href{mailto:machaka.mohammad@gmail.com}{machaka.mohammad@gmail.com}\\
\href{https://www.linkedin.com/in/mohammad-machaka-a63685172}{linkedin.com/in/mohammad-machaka-a63685172}\\[12pt]
\href{https://mohammad.machaka.net}{mohammad.machaka.net}\\[12pt]

\textbf{To:} Airbus Group, Achats digitaux\\
Marignane, France\\[6pt]
\textbf{Date:} \today\\[12pt]

\textbf{Subject:} Candidature Stage en Achats digitaux\\[12pt]

%==================== BODY =====================
Your digital purchasing internship hit home. I shape clear processes, living handbooks, and simple tools teams use. At Airbus I standardized HR reporting and cut deployments from one week to one day with templates and quality gates. At Green Praxis I run data and cloud platforms, document interfaces, and turn needs into guides and runbooks. This fits modeling the Buyers handbook, a useful G Site, and day to day buyer support.

I work in English and French and enjoy multi site collaboration. I bring web mastering, Apps Script, and project habits from CI CD and Git workflows. I am available April 2026 till October 2026. I’d welcome the chance to discuss how I could support your team. If that convenes you, you can find my availability on this calendar: \href{https://calendly.com/machaka-mohammad/30min}{calendly.com/machaka-mohammad/30min}).

\vspace{6pt}
Sincerely,\\[2pt]
\textbf{Mohammad Machaka}

\end{document}